Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd

transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
#transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
#transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)

@@

sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
#sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
#sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)

@@

AR_expanded_taken <- my_apriori(transactions_expanded)
# creating vector of fail course
#course_id_fail <- d_transactions_expanded %>%filter(PF == "fail") %>%distinct(`item_PF`)
#AR_expanded_PF <- my_apriori(transactions_expanded_PF,appearance = list(both = course_id_fail$`item_PF`))

@@

```
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
     AR_expanded_taken, 
     #AR_expanded_PF, AR_expanded_HL, 
     AR_expanded_Grade,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
   AR_expanded_taken, 
   #AR_expanded_PF, AR_expanded_HL, 
   AR_expanded_Grade)
```

@@

  ) %>%
  ungroup() %>%
    mutate_at(
      c("support",
        "confidence","confidence.old", "lift.old"),
      funs(round(., 5))
    )

@@

SR_expanded_taken   <- my_SR(data = sequences_expanded   )
##pass/fail filter
#SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% filter(`RHS Quality`=="fail")
##high/low filter
#SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% filter(`RHS Quality`=="low")

@@

    SR_expanded_taken, 
    #SR_expanded_PF, SR_expanded_HL, 
    SR_expanded_Grade,

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   sequences_expanded, 
   #sequences_expanded_PF, sequences_expanded_HL, 
   sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL, SR_Grade,
   SR_expanded_taken, 
  # SR_expanded_PF, SR_expanded_HL, 
   SR_expanded_Grade)

>>>>

#transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
#transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
#transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)

@@

#sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
#sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
#sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)

@@

#AR_expanded_taken <- my_apriori(transactions_expanded)
# creating vector of fail course
#course_id_fail <- d_transactions_expanded %>%filter(PF == "fail") %>%distinct(`item_PF`)
#AR_expanded_PF <- my_apriori(transactions_expanded_PF,appearance = list(both = course_id_fail$`item_PF`))

@@

```
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
     #AR_expanded_taken, 
     #AR_expanded_PF, AR_expanded_HL, 
     AR_expanded_Grade,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
   #AR_expanded_taken, 
   #AR_expanded_PF, AR_expanded_HL, 
   AR_expanded_Grade)
```

@@

  ) %>%
  ungroup() %>%
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    )

@@

#SR_expanded_taken   <- my_SR(data = sequences_expanded   )
##pass/fail filter
#SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% filter(`RHS Quality`=="fail")
##high/low filter
#SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% filter(`RHS Quality`=="low")

@@

    #SR_expanded_taken, 
    #SR_expanded_PF, SR_expanded_HL, 
    SR_expanded_Grade,

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   #sequences_expanded, 
   #sequences_expanded_PF, sequences_expanded_HL, 
   sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL, SR_Grade,
   #SR_expanded_taken, 
  # SR_expanded_PF, SR_expanded_HL, 
   SR_expanded_Grade)
